---
layout: post
title:  "Brazil's Macroeconomics"
date:   2021-05-17
description: This post presents important features of the Brazilian economy macroeconomic system.
---

```{r setup, include=FALSE}

library(tis)
library(cowplot)
library(readxl)
library(xlsx)
library(urca)
library(dynlm)

library(heatmaply)
library(kableExtra)
library(reshape)
library(reshape2)
library(plotly)

library(Hmisc)
library(dplyr)
require(gridExtra)
library(tibble)

library(hrbrthemes)
library(viridis)
library(plotly)
#library(d3heatmap)

require(gplots)
require(RColorBrewer)
require(heatmaply)
library(data.table)
library(ggplot2)
library(magrittr)
library(plyr)
library(ggpubr)

library(tidyverse)
library(ggraph)
library("ggplot2")
library("plyr")
library("scales")
library("likert")
library("ggsci")
library("sfcr")


knitr::opts_chunk$set(echo=TRUE)
load(paste0(getwd(),"/SNADATA.RData"))

```

## R Markdown

This webpage shows key macroeconomic features of Brazilian economy. These features were mostly studied during my Ph.D project. Understanding them helps to understand economic cycles and growth.




## Agents and transactions

In order to understand the macroeconomic features we need to ask which are the agents and how they earn and expend their financial inflows.

Agents are classifiend in accordance with the Brazilian Institute of Geography and Statistics (IBGE) as:

1. Households
2. Non-Financial Corporations
3. Financial Corporations
4. Government
5. Foreing Sector


The agents relate to eachother through two channels: a) transactions, and b) balance sheet.

Let's first check-out which are the transaction. With some cleaning procedures below we illustrate their average values in relation to GDP: 




```{r first, anchor="figure", fig.cap = "**Economic Transactions (% GDP)** ",fig.align='center', echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

d3 %>%  
  
  ggplot( aes(x = reorder(names, -mean),
              y = mean,
              fill=mean)) +
  
  
  geom_bar(stat = "identity")+
  

  
  geom_errorbar(aes(ymin=min, ymax=max),
                width=.2) +
  
  
  
  coord_flip()+
  
  scale_fill_gradient2(low=LtoM(4), mid='snow3', 
                       high=MtoH(4), space='Lab')+
  
  labs(fill="%")+
  
  
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank(),
        axis.ticks.x=element_blank(),
        panel.background = element_rect(fill = "white", colour = "white",
                                        size = 2, linetype = "solid"),
        panel.grid.major = element_line(size = 0.1, linetype = 'solid',
                                        colour = "grey96") 
  )

```